### 2011-11-04 docs/src/currydoc.tex
Markdown lib and doc added

The documentation comment for the module (i.e., the documentation
comment at the beginning of the module before the module header)
can be formatted with a subset of
\href{http://en.wikipedia.org/wiki/Markdown}{Markdown's syntax}\index{markdown}.
For instance, it can contain Markdown annotations for
emphasizing elements (e.g., \verb!*emph*! or \verb!_verb_!),
strong elements (e.g., \verb!**important**! or \verb!__important__!),
code elements (e.g., \verb!`3+4`!), code blocks (lines prefixed by four blanks),
unordered lists (lines prefixed by two blanks followed by ``\verb!* !''),
ordered lists (lines prefixed by two blanks followed by a digit and a dot),
quotations (lines prefixed by ``\verb!> !''),
and web links of the form \ccode{<http://\ldots>}
or \ccode{[link text](http://\ldots)}.
If the Markdown syntax should not be used, one could run CurryDoc
with the parameter \ccode{--nomarkdown}.

>>>>

The documentation comment for the module (i.e., the documentation
comment at the beginning of the module before the module header)
can be formatted with a subset of
\href{http://en.wikipedia.org/wiki/Markdown}{Markdown's syntax}\index{markdown}
(which is described in detail in the appendix).
For instance, it can contain Markdown annotations for
emphasizing elements (e.g., \verb!_verb_!),
strong elements (e.g., \verb!**important**!),
code elements (e.g., \verb!`3+4`!), code blocks (lines prefixed by four blanks),
unordered lists (lines prefixed by  ``\verb! * !''),
ordered lists (lines prefixed by blanks followed by a digit and a dot),
quotations (lines prefixed by ``\verb!> !''),
and web links of the form \ccode{<http://\ldots>}
or \ccode{[link text](http://\ldots)}.
If the Markdown syntax should not be used, one could run CurryDoc
with the parameter \ccode{--nomarkdown}.
